Northern Pikeminnow Abundance in Deadwater Slough, Salmon River, Idaho, and Potential Impacts to Local Chinook Salmon Populations

### 2022-04-11 analysis/paper/paper.Rmd
edits from KS

Predation on emigrating juvenile salmonids by piscivorous fishes is a widely-studied source of mortality within reservoirs and dam tailraces in the Columbia River basin. Native Northern Pikeminnow have been estimated to consume \~8% of the approximately 200 million juvenile salmonids emigrating through the lower Snake and Columbia rivers, annually. Less is known about the interaction between upstream, river-dwelling Northern Pikeminnow and their impacts on salmonid recovery above the reservoir systems. In this study, we examine the abundance of Northern Pikeminnow in a slow-water reach of the Salmon River, Idaho, known as Deadwater Slough, and consider their potential impacts on local Chinook Salmon populations. The Deadwater Slough is within a migration corridor for several Chinook Salmon populations as well as other Endangered Species Act-listings including steelhead and Sockeye Salmon. We estimated the abundance of Northern Pikeminnow in Deadwater Slough, an approximately 1.9 kilometer reach of the Salmon River, to be 19,499 in the fall and 10,352 in the spring, corresponding with the peak emigrations of juvenile Chinook Salmon. Using these abundance values, we estimated Northern Pikeminnow consumption of juvenile Chinook Salmon. Assuming 60% of the Northern Pikeminnow diet is fish, of which 50% is juvenile Chinook Salmon, we estimated the Northern Pikeminnow population can consume 61,409 juvenile Chinook Salmon, annually. Using a sensitivity analysis, estimated Northern Pikeminnow predation on juvenile Chinook Salmon was equivalent to 377 (95% CI: 161 - 935) returning adults. Given the relatively small size of the Salmon River, the large densities and potential consumption rates of Northern Pikeminnow in Deadwater Slough suggest predation likely has consequential impact on Chinook Salmon recovery in the Upper Salmon River.

@@

In this study, we estimated the abundance of Northern Pikeminnow in the Deadwater Slough and evaluated potential impacts to juvenile salmon emigrants, focusing on DSR and NRR Chinook Salmon. We hypothesize that high densities of piscivorous predators in the Deadwater Slough may explain the reduced survival observed for juvenile Chinook Salmon. To test this, our objectives were four-fold:

@@

During the fall DSR emigration, we estimated an average-size Northern Pikeminnow (`r round(avg_fall_NPM_TL, 1)` TL mm) to consume `r bio_g_summ$cumm_g[bio_g_summ$season == "Fall" & bio_g_summ$name == "f60_g"]` g of fish to maintain their body size, assuming 60% of their diet consists of fish prey (Figure \@ref(fig:bio-p)). Fall consumption ranged from `r bio_g_summ$cumm_g[bio_g_summ$season == "Fall" & bio_g_summ$name == "f30_g"]` g for a diet of 30% fish to `r bio_g_summ$cumm_g[bio_g_summ$season == "Fall" & bio_g_summ$name == "f90_g"]` g for a diet of 90% fish. During the spring NRR emigration, we estimated an average-size Northern Pikeminnow (`r round(avg_spring_NPM_TL, 1)` TL mm) to consume `r bio_g_summ$cumm_g[bio_g_summ$season == "Spring" & bio_g_summ$name == "f60_g"]` g of fish, assuming 60% of their diet is fish prey (Figure \@ref(fig:bio-p)). Spring consumption ranged from `r bio_g_summ$cumm_g[bio_g_summ$season == "Spring" & bio_g_summ$name == "f30_g"]` for a diet of 30% fish to `r bio_g_summ$cumm_g[bio_g_summ$season == "Spring" & bio_g_summ$name == "f90_g"]` for a diet of 90% fish. Daily consumption rates were higher early in the fall and late in the spring and corresponded with water temperatures above 8 degrees Celsius (Figure \@ref(fig:bio-p)). Given estimated mean Northern Pikeminnow population sizes of `r prettyNum(mean(all_est$N[all_est$model == "Schnabel - Delayed Mixing"]), big.mark = ",")` in the fall and `r prettyNum(round(spring_abund$N_S), big.mark = ",")` in the spring 2021, and a diet consisting of 60% fish, the Northern Pikeminnow population is estimated to consume `r round(tot_g_DSR, 1)` metric tons of fish during the fall DSR emigration and `r round(tot_g_NRR, 1)` metric tons during the spring NRR emigration in Deadwater Slough.

@@

Given yearly fish consumption estimates during the fall DSR and spring NRR periods, we produced a sensitivity analysis to calculate the consumption of juvenile Chinook Salmon where 30%, 50%, and 65% of total fish prey consumed are juvenile Chinook Salmon (Figure \@ref(fig:juv-con-p)). At the median value of 50%, we estimated that `r prettyNum(round(total_impacts$juv_N[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")` (95% CI: `r prettyNum(round(total_impacts$juv_Lci[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")` - `r prettyNum(round(total_impacts$juv_Uci[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")`) juvenile Chinook Salmon would be consumed. Using the median Granite-to-Granite SAR for Chinook Salmon in the Upper Salmon River, we estimated the "adult equivalents" of juveniles consumed to be `r prettyNum(round(total_impacts$adult_N[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")` (95% CI: `r prettyNum(round(total_impacts$adult_Lci[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")` - `r prettyNum(round(total_impacts$adult_Uci[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")`) adults (Figure \@ref(fig:adult-imp-p)).

@@

Several assumptions in our estimators may have influenced the magnitude of our abundance results. First, all models assumed a closed population; however, it is possible that immigration and emigration occurred. Nevertheless, our estimators still provide unbiased estimates of abundance assuming the immigration and emigration rates are equal between marked and unmarked fish. Emigration of marked individuals could reduce the marking fraction in the population leading to an upward bias in abundance estimates, but emigration rates would need to be substantial. We also captured two fish with marks from previous years, indicating seasonal residency of some fish. The multiple census estimators, which we report, are more robust to this assumption because the marking fraction is estimated daily. We additionally have little reason to believe that emigration occurs during the two-week survey window owing to favorable habitat for Northern Pikeminnow in Deadwater Slough relative to adjacent reaches. Given the size of the sampling area and the short duration of our surveys, the closed population assumption is likely met. This assumption can likewise affect results if mortality occurs for some marked fish released back to the population. During field processing, no mortalities or injury post release was observed and fish injured prior to release were retained. Nevertheless, the potential for mortality amongst marked and released fish cannot be discounted.

Next, our abundance estimates assumed that capture and recapture events are random samples of the population. Angling methods often have a size selection bias, thereby limiting abundance estimates to a size range susceptible to angling, resulting in a conservative estimate of the total population. We also question the validity of our assumption of equal catchability of individual fish between sampling events. Two individual fish were recaptured during multiple days within a survey, indicating that marked fish were continually susceptible to angling. We additionally suspect that marked and released fish may not have immediately mixed thoroughly back into the population. Although we attempted to release marked fish evenly throughout Deadwater Slough, we anecdotally observed anglers congregating in particular areas of the slough to socialize or exploit "good" fishing locales. Violations of the assumption of equal catchability between marked and unmarked fish may lead to an overestimate of abundance of Northern Pikeminnow in our study if marked fish have lower catchability. This bias will be proportional to the difference in catchability of marked and unmarked fish. As an example, if marked fish were only 70% as likely to be caught as unmarked fish, the true abundance is closer to 70% of our abundance estimate. This would additionally account for marked and released fish being "hook shy" for a period of time. The adjusted delayed-mixing Schnabel estimator may account for these biases; however the magnitude of bias is unknown.

@@

Although the origins of Deadwater Slough are somewhat ambiguous [@Reichmuth1985; @USACE1986], it is likely that human activities in Dump Creek appear to have either exacerbated or contributed to its formation, and in turn, created favorable conditions for Northern Pikeminnow. Among the three surveys, our lowest population abundance estimate was greater than 10,000 Northern Pikeminnow that occupy Deadwater Slough, suggesting a remarkably high density given the size of the area. The slow water velocity and lack of cover for fish also create conditions where juvenile salmonids that are rearing in or emigrating through Deadwater Slough, including Chinook Salmon, are susceptible to predation. We estimate that, at a minimum, Northern Pikeminnow in Deadwater Slough consume greater than `r prettyNum(round(min(total_impacts$juv_Lci), -3), big.mark = ",")` juvenile Chinook Salmon (the lower endpoint of the confidence interval for the most conservative scenario); however, it is likely that this value is closer to `r prettyNum(round(total_impacts$juv_N[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50], -3), big.mark = ",")`, annually. The magnitude of predation by Northern Pikeminnow is equivalent to `r round((min(total_impacts$adult_N) / 558) * 100)`% and `r round((max(total_impacts$adult_N) / 558) * 100)`% of recent adult escapements. Deadwater Slough predates the ESA-listing of Chinook Salmon populations in the Upper Salmon MPG in the 1990s and is therefore unlikely to be the primary cause for the population's decline. However, predation by Northern Pikeminnow in Deadwater Slough and elsewhere should be considered among limiting factors hindering recovery efforts of ESA-listed Chinook Salmon populations in the Upper Salmon MPG.

@@

```{r bio-tbl}
bio_tbl = bio_g_summ %>%
  mutate(`Date Range` = season) %>%
  select(season,
         `Date Range`,
         name,
         cumm_g) %>%
  mutate(name = str_sub(name, 2, 3)) %>%
  rename(Season = season,
         `% Fish in Diet` = name,
         `g Consumed` = cumm_g) %>%
  mutate(`Date Range` = recode(`Date Range`,
                               Fall = "Sep 15 - Nov 30",
                               Spring = "Mar 1 - May 31")) %>%
  kable(booktabs = T,
        caption = "Bioenergetics model runs to estimate the grams of fish consumed during the fall DSR and spring NRR Chinook Salmon emigrations. The date ranges for each model run, the assumed proportion of fish in the diet, and the total grams of fish consumed by an individual Northern Pikeminnow to maintain its body weight for a given season are shown. Northern Pikeminnow start and end weights were 598.7 and 430.7 g for the fall and spring seasons, respectively.") %>%
  kable_styling()

@@

```{r gastric-tab}
gastric_tbl %>%
  rename(Survey = event_name,
         Captured = captured,
         Lavaged = lavaged,
         'Stomach Contents' = stmch_contents,
         'Fish Contents' = fish_contents) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Summary of gastric lavage results including counts of the total number of Northern Pikeminnow captured, gastric lavaged, individuals with stomach contents, and individuals with fish prey contents.") %>%
  kable_styling()

@@

pTemp = bio_results %>%
  ggplot(aes(ymd, temperature_c)) +
  geom_line(color = "navyblue",
            size = 1.15) +
  theme_bw() +
  labs(y = expression("Water temp"*~degree*C),
       x = "Month",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_blank(),
        axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 0.1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.2, .3, .1, .1), "cm"))

@@

```{r juv-con-p, fig.cap = "Estimated number of juvenile Chinook Salmon consumed by Northern Pikeminnow from a sensitivity analysis of variable diet scenarios. The proportion of Chinook Salmon in the total fish prey consumed by Northern Pikeminnow were evaluated for 30%, 50%, and 65% scenarios, similar to those reported by Zimmerman and Ward 1999."}

juv_cons_p = impact_df %>%
  select(season,
         perc_diet,
         p_chnk,
         N = juv_N,
         Lci = juv_Lci,
         Uci = juv_Uci) %>%
  group_by(perc_diet,
           p_chnk) %>%
  summarise(across(c("N", "Lci", "Uci"),sum),
            .groups = "drop") %>%
  mutate(Stage = "Juveniles") %>%
  mutate(p_chnk = p_chnk * 100) %>%
  rename(perc_chnk = p_chnk) %>%
  ggplot(aes(x = perc_diet,
             y = N / 1000,
             group = as.factor(perc_chnk),
             color = as.factor(perc_chnk))) +
  geom_point(size = 2) +
  geom_line(size = 1.1) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  scale_color_manual(name = "Percent Chinook", 
                     values=c("lightsteelblue","steelblue3","navyblue")) +
  theme(axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black"),
        legend.position = c(.19, .89),
        legend.background = element_blank(),
        legend.key.size = unit(.56, "cm"),
        legend.box = 'horizontal') +
  labs(y = "Juvenile Chinook Consumed (x 1,000)", 
       x = "Percent Fish in Pikeminnow Diet")

>>>>

Predation on emigrating juvenile salmonids by piscivorous fishes is a widely-studied source of mortality within reservoirs and dam tailraces in the Columbia River basin. Native Northern Pikeminnow have been estimated to consume \~8% of the approximately 200 million juvenile salmonids emigrating through the lower Snake and Columbia rivers, annually. Less is known about the interaction between upstream, river-dwelling Northern Pikeminnow and their impacts on salmonid recovery above the reservoir systems. In this study, we examine the abundance of Northern Pikeminnow in a slow-water reach of the Salmon River, Idaho, known as Deadwater Slough, and consider their potential impacts on local Chinook Salmon populations. The Deadwater Slough is within a migration corridor for several Chinook Salmon populations as well as other Endangered Species Act-listings including steelhead and Sockeye Salmon. We estimated the abundance of Northern Pikeminnow in Deadwater Slough, an approximately 1.9 kilometer reach of the Salmon River, to be 19,499 in the fall and 10,352 in the spring, corresponding with the peak emigration windows of juvenile Chinook Salmon. Using these abundance values, we estimated Northern Pikeminnow consumption of juvenile Chinook Salmon. Assuming 60% of the Northern Pikeminnow diet is fish, of which 50% is juvenile Chinook Salmon, we estimated the Northern Pikeminnow population can consume 61,409 juvenile Chinook Salmon, annually. After performing a sensitivity analysis, we estimated Northern Pikeminnow predation on juvenile Chinook Salmon was equivalent to 377 (95% CI: 161 - 935) returning adults. Given the relatively small size of the Salmon River, the large densities and potential consumption rates of Northern Pikeminnow in Deadwater Slough suggest predation likely has a consequential impact on Chinook Salmon recovery in the Upper Salmon River.

@@

In this study, we estimated the abundance of Northern Pikeminnow in the Deadwater Slough and evaluated potential impacts to juvenile salmon emigrants, focusing on DSR and NRR Chinook Salmon. We hypothesized that high densities of piscivorous predators in the Deadwater Slough might explain the reduced survival observed for juvenile Chinook Salmon. To test this, our objectives were four-fold:

@@

During the fall DSR emigration, we estimated an average-size Northern Pikeminnow (`r round(avg_fall_NPM_TL, 1)` TL mm) to consume `r bio_g_summ$cumm_g[bio_g_summ$season == "Fall" & bio_g_summ$name == "f60_g"]` g of fish to maintain their body size, assuming 60% of their diet consisted of fish prey (Figure \@ref(fig:bio-p)). Fall consumption ranged from `r bio_g_summ$cumm_g[bio_g_summ$season == "Fall" & bio_g_summ$name == "f30_g"]` g for a diet of 30% fish to `r bio_g_summ$cumm_g[bio_g_summ$season == "Fall" & bio_g_summ$name == "f90_g"]` g for a diet of 90% fish. During the spring NRR emigration, we estimated an average-size Northern Pikeminnow (`r round(avg_spring_NPM_TL, 1)` TL mm) to consume `r bio_g_summ$cumm_g[bio_g_summ$season == "Spring" & bio_g_summ$name == "f60_g"]` g of fish, assuming 60% of their diet was fish prey (Figure \@ref(fig:bio-p)). Spring consumption ranged from `r bio_g_summ$cumm_g[bio_g_summ$season == "Spring" & bio_g_summ$name == "f30_g"]` for a diet of 30% fish to `r bio_g_summ$cumm_g[bio_g_summ$season == "Spring" & bio_g_summ$name == "f90_g"]` for a diet of 90% fish. Daily consumption rates were higher early in the fall and late in the spring and corresponded with water temperatures above 8 degrees Celsius (Figure \@ref(fig:bio-p)). Given estimated mean Northern Pikeminnow population sizes of `r prettyNum(mean(all_est$N[all_est$model == "Schnabel - Delayed Mixing"]), big.mark = ",")` in the fall and `r prettyNum(round(spring_abund$N_S), big.mark = ",")` in the spring 2021, and a diet consisting of 60% fish, the Northern Pikeminnow population was estimated to consume `r round(tot_g_DSR, 1)` metric tons of fish during the fall DSR emigration and `r round(tot_g_NRR, 1)` metric tons during the spring NRR emigration in Deadwater Slough.

@@

Given yearly fish consumption estimates during the fall DSR and spring NRR periods, we produced a sensitivity analysis to calculate the consumption of juvenile Chinook Salmon where 30%, 50%, and 65% of total fish prey consumed were juvenile Chinook Salmon (Figure \@ref(fig:juv-con-p)). At the median value of 50%, we estimated that `r prettyNum(round(total_impacts$juv_N[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")` (95% CI: `r prettyNum(round(total_impacts$juv_Lci[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")` - `r prettyNum(round(total_impacts$juv_Uci[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")`) juvenile Chinook Salmon would be consumed. Using the median Granite-to-Granite SAR for Chinook Salmon in the Upper Salmon River, we estimated the "adult equivalents" of juveniles consumed to be `r prettyNum(round(total_impacts$adult_N[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")` (95% CI: `r prettyNum(round(total_impacts$adult_Lci[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")` - `r prettyNum(round(total_impacts$adult_Uci[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50]), big.mark = ",")`) adults (Figure \@ref(fig:adult-imp-p)).

@@

Several assumptions in our estimators may have influenced the magnitude of our abundance results. First, all models assumed a closed population; however, it is possible that immigration and emigration occurred. Nevertheless, our estimators still provide unbiased estimates of abundance assuming the immigration and emigration rates were equal between marked and unmarked fish. Emigration of marked individuals could reduce the marking fraction in the population leading to an upward bias in abundance estimates, but emigration rates would have needed to be substantial. We also captured two fish with marks from previous years, indicating seasonal residency of some fish. The multiple census estimators, which we report, are more robust to this assumption because the marking fraction was estimated daily. We additionally have little reason to believe that emigration occurs during the two-week survey window owing to favorable habitat for Northern Pikeminnow in Deadwater Slough relative to adjacent reaches. Given the size of the sampling area and the short duration of our surveys, the closed population assumption was likely met. This assumption could likewise have affected results if mortality occurred for some marked fish released back to the population. During field processing, no mortalities or injuries post release were observed and fish injured prior to release were retained. Nevertheless, the potential for mortality amongst marked and released fish cannot be discounted.

Next, our abundance estimates assumed that capture and recapture events are random samples of the population. Angling methods often have a size selection bias, thereby limiting abundance estimates to a size range susceptible to angling, resulting in a conservative estimate of the total population. The estimators also assumed equal catchability of individual fish between sampling events; two fish were recaptured during multiple days within a survey, indicating that marked fish were continually susceptible to angling. It is also possible that marked and released fish may not have immediately mixed thoroughly back into the population. Although we attempted to release marked fish evenly throughout Deadwater Slough, we anecdotally observed anglers congregating in particular areas of the slough to socialize or exploit "good" fishing locales. Violations of the assumption of equal catchability between marked and unmarked fish may have led to an overestimate of abundance of Northern Pikeminnow in our study if marked fish have lower catchability. This bias will be proportional to the difference in catchability of marked and unmarked fish. As an example, if marked fish were only 70% as likely to be caught as unmarked fish, the true abundance is closer to 70% of our abundance estimate. This would additionally account for marked and released fish being "hook shy" for a period of time. The adjusted delayed-mixing Schnabel estimator may account for these biases; however the magnitude of bias is unknown.

@@

Although the origins of Deadwater Slough are somewhat ambiguous [@Reichmuth1985; @USACE1986], it is likely that human activities in Dump Creek appear to have either exacerbated or contributed to its formation, and in turn, created favorable conditions for Northern Pikeminnow. Among the three surveys, our lowest population abundance estimate was greater than 10,000 Northern Pikeminnow occupying Deadwater Slough, suggesting a remarkably high density given the size of the area. The slow water velocity and lack of cover for fish also create conditions where juvenile salmonids that are rearing in or emigrating through Deadwater Slough, including Chinook Salmon, are susceptible to predation. We estimate that, at a minimum, Northern Pikeminnow in Deadwater Slough consume greater than `r prettyNum(round(min(total_impacts$juv_Lci), -3), big.mark = ",")` juvenile Chinook Salmon (the lower endpoint of the confidence interval for the most conservative scenario); however, it is likely that this value is closer to `r prettyNum(round(total_impacts$juv_N[total_impacts$perc_diet == 60 & total_impacts$p_chnk == 0.50], -3), big.mark = ",")`, annually. The magnitude of predation by Northern Pikeminnow is equivalent to `r round((min(total_impacts$adult_N) / 558) * 100)`% and `r round((max(total_impacts$adult_N) / 558) * 100)`% of recent adult escapements. Deadwater Slough predates the ESA-listing of Chinook Salmon populations in the Upper Salmon MPG in the 1990s and is therefore unlikely to be the primary cause for the population's decline. However, predation by Northern Pikeminnow in Deadwater Slough and elsewhere should be considered among limiting factors hindering recovery efforts of ESA-listed Chinook Salmon populations in the Upper Salmon MPG.

@@

```{r bio-tbl}
bio_tbl = bio_g_summ %>%
  mutate(`Date Range` = season) %>%
  select(season,
         `Date Range`,
         name,
         cumm_g) %>%
  mutate(name = str_sub(name, 2, 3)) %>%
  rename(Season = season,
         `Percent Fish in Diet` = name,
         `g Fish Consumed` = cumm_g) %>%
  mutate(`Date Range` = recode(`Date Range`,
                               Fall = "Sep 15 - Nov 30",
                               Spring = "Mar 1 - May 31")) %>%
  kable(booktabs = T,
        caption = "Bioenergetics model runs to estimate the grams of fish consumed during the fall DSR and spring NRR Chinook Salmon emigrations. The date ranges for each model run, the assumed proportion of fish in the diet, and the total grams of fish consumed by an individual Northern Pikeminnow to maintain its body weight for a given season are shown. Northern Pikeminnow start and end weights were 598.7 and 430.7 g for the fall and spring seasons, respectively.") %>%
  kable_styling()

@@

```{r gastric-tab}
gastric_tbl %>%
  rename(Survey = event_name,
         Captured = captured,
         Lavaged = lavaged,
         'Stomach Contents' = stmch_contents,
         'Fish Contents' = fish_contents) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Counts of the total number of Northern Pikeminnow captured, gastric lavaged, individuals with stomach contents, and individuals with fish prey contents.") %>%
  kable_styling()

@@

pTemp = bio_results %>%
  ggplot(aes(ymd, temperature_c)) +
  geom_line(color = "black",
            size = 1.15) +
  theme_bw() +
  labs(y = expression("Water temp"*~degree*C),
       x = "Month",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_blank(),
        axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 0.1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.2, .3, .1, .1), "cm"))

@@

```{r juv-con-p, fig.cap = "Estimated number of juvenile Chinook Salmon consumed by Northern Pikeminnow from a sensitivity analysis of diet scenarios made up of variable percentages of fish. The proportion of Chinook Salmon in the total fish prey consumed by Northern Pikeminnow were evaluated for 30%, 50%, and 65% scenarios, similar to those reported by Zimmerman and Ward 1999."}

juv_cons_p = impact_df %>%
  select(season,
         perc_diet,
         p_chnk,
         N = juv_N,
         Lci = juv_Lci,
         Uci = juv_Uci) %>%
  group_by(perc_diet,
           p_chnk) %>%
  summarise(across(c("N", "Lci", "Uci"),sum),
            .groups = "drop") %>%
  mutate(Stage = "Juveniles") %>%
  mutate(p_chnk = p_chnk * 100) %>%
  rename(perc_chnk = p_chnk) %>%
  ggplot(aes(x = perc_diet,
             y = N / 1000,
             group = as.factor(perc_chnk),
             color = as.factor(perc_chnk))) +
  geom_point(size = 2) +
  geom_line(size = 1.1) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  scale_color_manual(name = "Percent Chinook", 
                     values=c("gray70", "gray35","gray0")) +
  theme(axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black"),
        legend.position = c(.19, .89),
        legend.background = element_blank(),
        legend.key.size = unit(.56, "cm"),
        legend.box = 'horizontal') +
  labs(y = "Juvenile Chinook Consumed (x 1,000)", 
       x = "Percent Fish in Pikeminnow Diet")
